### 2021-07-15 chapters/9_conclusion.tex
acr fuzzy c-means
styling issues

\chapter{Conclusion}
\label{ch:conclusion}
Our research started with comparing three mutation testing tools for Java and found that the state of the art was outdated.
We replicated the state of the art research with current data available on the mutation testing tools.
The state of art showed that two out of three mutation testing tools were not actively maintained anymore.
The mutation testing tool PIT scored best on the metrics measured in our replication study, this is also the tool we decided to use for our research.
\newline
We created a list of characteristics based on existing research. 
We then extended this list by identifying characteristic with logic and data available.
We used the identified characteristics to represent the mutants.
\newline
We clustered the mutants with two different clustering techniques; hierarchical clustering and by training a machine learning clustering model.
The hierarchical clustering showed that we can cluster mutants while maintaining effectiveness.
We achieved reductions of up to 75\% of the total amount of mutants without significantly reducing the accuracy.
\newline
The machine learning model showed a significant reduction in effectiveness.
We trained the machine learning model with parameters that were optimal according to existing research. 
We also used a machine learning model, specialized in calculating the number of clusters for fuzzy clustering, to calculate the number of clusters.
While the minimum clustering accuracy was higher than that of the hierarchical clustering, the maximum cluster accuracy was lower than that of the hierarchical clustering.
The cluster accuracy had a greater impact on the clusters of the machine learning model because there was a relatively small number of clusters.
Our research proves that it is possible to determine the means of domains as the centre of a cluster within a programming language without narrowing down the scope to specific pieces of code.
It can be applied to all Java projects that can be run with PIT. 
Which is a larger scope than in existing mutation clustering research.

\section{Future work}
\label{sec:future_work}
\subsubsection{Optimizing parameters of machine learning model}
We trained the machine learning model with specific parameters guided by science. 
These proved to be non optimal for our purpose.
This research can be extended by finding the optimal parameters for the fuzzy c-means clustering algorithm.
The results showed a higher minimum accuracy which can indicate that there is potential for clustering the mutants with the machine learning model.
Further research and fine-tuning is required to find out if the model can be trained to achieve more accurate scores.

>>>>

\chapter{Conclusion}
\label{ch:conclusion}
Our research started with comparing three mutation testing tools for Java and found that the state of the art was outdated.
We replicated the state of the art research with current data available on the mutation testing tools.
The state of art showed that two out of three mutation testing tools were not actively maintained anymore.
The mutation testing tool PIT scored best on the metrics measured in our replication study, this is also the tool we decided to use for our research.
\newline
We created a list of characteristics based on existing research. 
We then extended this list by identifying characteristic with logic and data available.
We used the identified characteristics to represent the mutants.
\newline
We clustered the mutants with two different clustering techniques; hierarchical clustering and by training a machine learning clustering model.
The hierarchical clustering showed that we can cluster mutants while maintaining effectiveness.
We achieved reductions of up to 75\% of the total amount of mutants without significantly reducing the accuracy.
\newline
The machine learning model showed a significant reduction in effectiveness.
We trained the machine learning model with parameters that were optimal according to existing research. 
We also used a machine learning model, specialized in calculating the number of clusters for fuzzy clustering, to calculate the number of clusters.
While the minimum clustering accuracy was higher than that of the hierarchical clustering, the maximum cluster accuracy was lower than that of the hierarchical clustering.
The cluster accuracy had a larger impact on the clusters of the machine learning model because there was a relatively small number of clusters.
Our research proves that it is possible to determine the means of domains as the centre of a cluster within a programming language without narrowing down the scope to specific pieces of code.
It can be applied to all Java projects that can be run with PIT. 
Which is a larger scope than in existing mutation clustering research.

\section{Future work}
\label{sec:future_work}
\subsubsection{Optimizing parameters of machine learning model}
We trained the machine learning model with specific parameters guided by science. 
These proved to be non optimal for our purpose.
This research can be extended by finding the optimal parameters for the \acrshort{som} clustering algorithm.
The results showed a higher minimum accuracy which can indicate that there is potential for clustering the mutants with the machine learning model.
Further research and fine-tuning is required to find out if the model can be trained to achieve more accurate scores.

### 2021-07-15 chapters/rq2/1_experiment_design.tex
styling issues

\subsubsection{ART models}
ART models are characterized by systems of differential equations that formulate stable self-organizing learning methods\cite{Du2010Clustering:Approach}.
The stability and plasticity properties as well as the ability to efficiently process dynamic data make the ART attractive for clustering large, rapidly changing sequences of input patterns\cite{Du2010Clustering:Approach}.
While the ART models are very good at what they do, they do not fit our purpose of clustering mutants.
As described above the ART models expect rapidly changing sequences of input patterns.
Our data does not contain binary input patterns and it is also not rapidly changing.
Therefore we will not select an ART model.

@@

\subsubsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled variables in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was very stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also observe  that their results partially overlap with other research in the same domain.
\newline
Based the conclusions made by Mingoti et al., we can conclude that the \acrshort{fcm} model has the best performance overall.
Thus for this experiment we select the \acrshort{fcm} model.

>>>>

\subsubsection{ART models}
ART models are characterized by systems of differential equations that formulate stable self-organizing learning methods\cite{Du2010Clustering:Approach}.
The stability and plasticity properties as well as the ability to efficiently process dynamic data make the ART attractive for clustering large, rapidly changing sequences of input patterns\cite{Du2010Clustering:Approach}.
While the ART models are good at what they do, they do not fit our purpose of clustering mutants.
As described above the ART models expect rapidly changing sequences of input patterns.
Our data does not contain binary input patterns and it is also not rapidly changing.
Therefore we will not select an ART model.

@@

\subsubsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled variables in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also observe  that their results partially overlap with other research in the same domain.
\newline
Based the conclusions made by Mingoti et al., we can conclude that the \acrshort{fcm} model has the best performance overall.
Thus for this experiment we select the \acrshort{fcm} model.
